%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

% possible options include font size ('10pt', '11pt' and '12pt'), 
% paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape')
% and font family ('sans' and 'roman')
\documentclass[10pt,a4paper,sans]{moderncv}        

% moderncv themes

% style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvstyle{classic}                             

% color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\moderncvcolor{black}                               

% to set the default font; use '\sfdefault' for the default sans serif font,
% '\rmdefault' for the default roman one, or any tex font name
%\renewcommand{\familydefault}{\sfdefault}         

% uncomment to suppress automatic page numbering for CVs longer than one page
%\nopagenumbers{}                                  

% character encoding
% if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage[utf8]{inputenc}                       

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% if you want to change the width of the column with the dates
%\setlength{\hintscolumnwidth}{3cm}                

% for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks.
% be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
%\setlength{\makecvtitlenamewidth}{10cm}           

% personal data
\name{Garrett}{Barboza}

% \title{}               

% the "postcode city" and "country" arguments can be omitted or provided empty
\address{550 14th Road South. Apt. 1420 }{Arlington, VA 22202}{United States}

\phone[mobile]{+1~(409)~422~7269}
\email{garrett@garrettbarboza.com}
\homepage{garrettbarboza.com}

%\social[linkedin]{john.doe}
%\social[twitter]{jdoe}
%\social[github]{jdoe}

%\extrainfo{additional information}

% '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it 
% (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\photo[64pt][0.4pt]{picture}                       

%\quote{Some quote}

\begin{document}

\makecvtitle

\section{Education}
\cventry{2009--2013}{BSc Computer Engineering}{Carnegie Mellon University}{Pittsburgh, PA}{}
{Minor in Computer Science}

\section{Experience}
\subsection{Vocational}
\cventry{October 2011--Present}{Cofounder \& Engineer}{Kaprica Security}{Reston, VA}{}
{Helped found and bootstrap a mobile security startup.
\begin{itemize}
\item Designed and built a hardware based solution for mobile platform security.
\item Ported initial solution to a variety of platforms for demoing purposes.
\item Developed embedded and backend code to provide an intuitive user experience.
\end{itemize}}

\cventry{Summer 2011}{Security Intern}{Lockheed Martin}{Arlington, VA}{}
{Worked in Internal Research and Development focusing on embedded systems from a security standpoint.}

\cventry{Summer 2010}{Software Engineering Intern}{Bay Controls}{Maumee, OH}{}
{Developed an Android application to remotely control internet enabled thermostats.
\begin{itemize}
\item Integrated application with existing infrastructure.
\item Solely responsible for development of Android application.
\end{itemize}}

\subsection{Miscellaneous}
\cventry{Spring 2013}{picoCTF}{Carnegie Mellon University}{Pittsburgh, PA}{}
{Designed and ran a capture the flag security competition for high school students.
\begin{itemize}
\item Over 5000 high school students competed during the course of a week.
\item Sponsored by the NSA
\end{itemize}}

\section{Skills}
\cvitem{Specialty}{Software Security, Systems Programming, Embedded Systems, Compilers}
\cvitem{Programming Languages}{C, Assembly, Python, Haskell, Javascript}

\section{Interests}
\cvitem{Programming Languages}{I am interested in research related to the design and implementation behind programming languages, specifically functional programming languages, and compiler construction.}
\cvitem{Reverse Engineering \& Vulnerability Research}{I am interested in the analysis of software and systems from a security perspective. Specifically, attack and defense techniques related to compiled binaries and operating systems.}
\end{document}
